---
title: "Bommeleeër Affär"
author: "Bryan Nelson"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
lang: "en-us"
---

<style>                     
.navbar {
  background-color:maroon;
  color:white;
}
</style>  

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(leaflet)
library(DT)
library(timevis)
library(crosstalk)
library(timelineS)

bomm <- read_csv("C:/Users/bryan/Dropbox/Computer/Andromeda-Tau/data-reflections/blog-data/bommeleeer-affar/data/bommeleeër-affär.csv")

bomm$Date <- mdy(bomm$Date)
```


Locations {data-icon="ion-map"}
========================================================

Column {.sidebar data-width=200}
-------------------------------------
<br/>
**Locations**

The Bommeleeër Affär, or Bomber's Affair, was a series of bomb attacks in Luxembourg between 30 May 1984 and 25 May 1986.

Some locations are approximate to the town or neighborhood of the attack.

**References**

[Bommeleeër News](https://www.rtl.lu/news/bommeleeer), RTL (Luxembourgish)

[Das Bommeleeër-Dossier](https://www.wort.lu/de/view/das-bommeleeer-dossier-5092c3a9e4b0fe37043e8be8), Luxemburger Wort (German)

DNA: Luxembourg Podcast: [Part One](https://today.rtl.lu/media/podcasts/a/1791097.html) and [Part Two](https://today.rtl.lu/media/podcasts/a/1791100.html), RTL (English)

Column {data-width=500}
-----------------------------------------------------------------------

### Map

```{r}
shared_bomm <- SharedData$new(bomm)
```


```{r}
filter_slider("Date", "Date", shared_bomm, column = ~Date)

expl_icon <- makeIcon(
  iconUrl = "https://cdn-icons-png.flaticon.com/512/831/831687.png",
  iconWidth = 24, iconHeight = 24)

leaflet() %>% 
  addTiles(group = "Map") %>%
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite") %>%
  addMarkers(data = shared_bomm,
             lat = ~latitude, lng = ~longitude,
             popup = ~paste0("Target: ", Target, "<br/>Location: ", Location, "<br/>Date: ", Date, "<br/>", Notes),
             label = ~Target,
             icon = expl_icon) %>%
  addLayersControl(baseGroups=c("Map", "Satellite"),
                   options=layersControlOptions(collapsed=FALSE))
```

Column {.tabset data-width=500}
-----------------------------------------------------------------------

### Table

```{r}
shared_bomm %>%
  datatable(rownames = FALSE, options = list(paging = FALSE, scrollY = FALSE))
```

Timeline {data-icon="ion-clock"}
========================================================

Column {.sidebar data-width=200}
-------------------------------------
<br/>
**Timeline**

The Bommeleeër Affär, or Bomber's Affair, was a series of bomb attacks in Luxembourg between 30 May 1984 and 25 May 1986.

**References**

[Bommeleeër News](https://www.rtl.lu/news/bommeleeer), RTL (Luxembourgish)

[Das Bommeleeër-Dossier](https://www.wort.lu/de/view/das-bommeleeer-dossier-5092c3a9e4b0fe37043e8be8), Luxemburger Wort (German)

DNA: Luxembourg Podcast: [Part One](https://today.rtl.lu/media/podcasts/a/1791097.html) and [Part Two](https://today.rtl.lu/media/podcasts/a/1791100.html), RTL (English)

Column {.tabset data-width=500}
-----------------------------------------------------------------------

### Timeline

```{r}
bomm %>%
  mutate(start = Date) %>%
  mutate(content = Target) %>%
  timevis()
```

Documents {data-icon="ion-document"}
========================================================

Column {.sidebar data-width=200}
-------------------------------------
<br/>
**Documents**

Few primary documents are in English, but a few of these are of particular interest: the ransom letters, though the English is likely not of a native speaker, and a review by the CIA in 1986.

**References**

[Bommeleeër News](https://www.rtl.lu/news/bommeleeer), RTL (Luxembourgish)

[Das Bommeleeër-Dossier](https://www.wort.lu/de/view/das-bommeleeer-dossier-5092c3a9e4b0fe37043e8be8), Luxemburger Wort (German)

DNA: Luxembourg Podcast: [Part One](https://today.rtl.lu/media/podcasts/a/1791097.html) and [Part Two](https://today.rtl.lu/media/podcasts/a/1791100.html), RTL (English)

Column {.tabset data-width=800}
-----------------------------------------------------------------------

### Bommeleeër Ransom Letters
![Bommeleeër Ransom Letters](documents/Erpresser-Breiwer.pdf){height=800 width=800}

### CIA Terrorism Review, 1986-02-10
![CIA Terrorism Reivew, 1986-02-10](documents/CIA-Terrorism-Review-1986-02-10.pdf){height=800 width=800}